Refining character relationships using embeddings of textual units : a case study on Les Misérables

### 2022-10-01 article/paper1.tex
write article

The first results in this section is to examine the most associated words with a subset of character-based objects, which can be found in Table 3 for \textbf{CA-CENT} and Table 4 for \textbf{CA-REG} with $\lambda = 0.01$. We see that with only 5 words, characters and relationships are summarized accurately. As expected, we see that the \textbf{CA-CENT} reveals its additive nature between characters and relationships: words used to describe a relationship rob off on their characters descriptions (see e.g. Cosette, Cosette-Marius, and Cosette-Valjean). By constrast, the \textbf{CA-REG} method displays more "perpendicular" descriptions of objects, with less words repeating. Note that we did not show here the least associated words with each object, as they are frequently the same and all related to the long description of the Battle of Waterloo in volume 2 ("infanterie", "wellington", "cuirassier", "bridage"), containing no protagonist of the story.

@@

	\label{CA_CENT_word_vs_obj}
	\caption{The 5 most associated words (similarity in parentheses) to objects regarding the \textbf{CA-CENT} method, for a selected set of characters and character pairs. Words appearing at least two times are in bold.}
\end{table*}

@@

	\label{CA_REG_word_vs_obj}
	\caption{The 5 most associated words (similarity in parentheses) to objects regarding the \textbf{CA-REG} method ($\lambda = 0.01$), for a selected set of characters and character pairs. Words appearing at least two times are in bold.}
\end{table*}

>>>>

@@

	\label{CA_CENT_word_vs_obj}
	\caption{The 5 most associated words (similarity in parentheses) to a selected set of characters and character pairs, regarding the \textbf{CA-CENT} method. Words appearing at least two times are in bold.}
\end{table*}

@@

	\label{CA_REG_word_vs_obj}
	\caption{The 5 most associated words (similarity in parentheses) to a selected set of characters and character pairs, regarding the \textbf{CA-REG} method ($\lambda = 0.01$). Words appearing at least two times are in bold.}
\end{table*}
¨
The first results in this section is to examine the most associated words with a subset of character-based objects, which can be found in Table 3 for \textbf{CA-CENT} and Table 4 for \textbf{CA-REG} with $\lambda = 0.01$. We see that with only 5 words, characters and relationships are summarized accurately. As expected, we see that the \textbf{CA-CENT} reveals its additive nature between characters and relationships: words used to describe a relationship rob off on their characters descriptions (see e.g. Cosette, Cosette-Marius, and Cosette-Valjean). By constrast, the \textbf{CA-REG} method displays more "perpendicular" descriptions of objects, with less words repeating. Note that we did not show here the least associated words with each object, as they are frequently the same and all related to the long description of the Battle of Waterloo in volume 2 ("infanterie", "wellington", "cuirassier", "bridage"), containing no protagonist of the story.

\begin{table*}[!bh]
	\centering
	\scalebox{0.9}{	
	\begin{tabular}{|c|c|c|c|}
		\hline
		aimer & rue & justice & guerre \\ \hline
		Dahlia-Fameuil (1.12) & Courfeyrac-Fauchelevent (0.79) & Azelma-Babet (1.09) & Combeferre-Fauchelevent (1.35) \\ \hline
		Dahlia-Listolier (1.12) & Courfeyrac-Toussaint (0.79) & Azelma-Brujon (1.09) & Feuilly-Valjean (1.27) \\ \hline
		Fameuil-Zéphine (1.12) & Eponine-Fauchelevent (0.79) & Azelma-Claquesous (1.09) & Feuilly-Marius (1.22) \\ \hline
		Listolier-Zéphine (1.12) & Eponine-Gavroche (0.79) & Azelma-Magnon (1.09) & Lesgle-Valjean (1.15) \\ \hline
		Gillenormand-Toussaint (1.11) & Eponine-Pontmercy (0.79) & Azelma-Montparnasse (1.09) & Mabeuf-Valjean (1.15) \\ \hline
	\end{tabular}
	}
	\label{CA_CENT_obj_words}
	\caption{The 5 most associated character-based objects (similarity in parentheses) to a selected set of words regarding the \textbf{CA-CENT} method.}
\end{table*}

\begin{table*}[!bh]
	\centering
	\scalebox{0.9}{	
		\begin{tabular}{|c|c|c|c|}
			\hline
			aimer & rue & justice & guerre \\ \hline
			Cosette-Marius (0.35) & Courfeyrac (0.37) & Javert-Valjean (0.37) & Grantaire-Pontmercy (0.94) \\ \hline
			Myriel (0.31) & Grantaire-Prouvaire (0.29) & Champmathieu-Valjean (0.37) & Grantaire (0.56) \\ \hline
			Basque-Fauchelevent (0.25) & Cosette-Javert (0.26) & Myriel (0.21) & Marius-Pontmercy (0.55) \\ \hline
			Myriel-Valjean (0.22) & Marius-Prouvaire (0.22) & Grantaire (0.18) & Pontmercy (0.55) \\ \hline
			Fauchelevent-Gillenormand (0.21) & Enjolras (0.22) & Grantaire-Javert (0.16) & Enjolras (0.49) \\ \hline
		\end{tabular}
	}
	\label{CA_REG_obj_words}
	\caption{The 5 most associated character-based objects (similarity in parentheses) to a selected set of words regarding the \textbf{CA-REG} method ($\lambda = 0.01$).}
\end{table*}
